---
title: "Dissertation Analysis"
output: html_notebook
---



```{r}
library(tidyverse)
library(reticulate)
library(readxl)
library(here)
library(solitude)
library(randomForest)
library(caTools)
library(caret)

here::i_am("red_flag_code.Rmd")
source(here("functions/sic_to_section_20210513.R"))
```


```{r}
# IMPORT DATA 

chain_features <- read_excel(here("data/sample_2_chain_features.csv"))
bvd_by_layer <- read_csv(here("data/sample_2_bvd_by_layer.csv.gz"))
country_by_layer <- read_csv(here("data/sample_2_country_by_layer.csv.gz"))
secrecy_scores <- read_excel(here("data/FSI-Rankings.xlsx"), sheet = "secrecy_scores")
late_filing <- read_excel(here("data/sample_2_late_filing_companies.xlsx"), sheet = "Results")
```

```{r}
# ADD COUNTRIES PRESENT IN CHAIN

# filter bvd for the correct terminal companies
bvd_by_layer <- bvd_by_layer %>%
  filter(layer0 %in% chain_features$terminal_bvd)

# filter country for the same ones
country_by_layer <- country_by_layer %>%
  filter(X1 %in% bvd_by_layer$X1)

# add terminal to then merge iso2 to chain features
terminal_bvd <- bvd_by_layer %>%
  select(X1, layer0) %>%
  rename(terminal_bvd = layer0)

# merge
country_by_layer <- country_by_layer %>%
  left_join(terminal_bvd)

# rename iso2 layers
country_by_layer <- country_by_layer %>%
  select(!c(X1, layer0)) %>%
  rename(layer1_iso2 = 1,
         layer2_iso2 = 2,
         layer3_iso2 = 3,
         layer4_iso2 = 4,
         layer5_iso2 = 5,
         layer6_iso2 = 6,
         layer7_iso2 = 7,
         layer8_iso2 = 8,
         layer9_iso2 = 9,
         layer10_iso2 = 10,
         layer11_iso2 = 11,
         layer12_iso2 = 12,
         layer13_iso2 = 13,
         layer14_iso2 = 14,
         layer15_iso2 = 15,
         layer16_iso2 = 16,
         layer17_iso2 = 17,
         layer18_iso2 = 18,
         layer19_iso2 = 19,
         layer20_iso2 = 20,
         layer21_iso2 = 21,
         layer22_iso2 = 22,
         layer23_iso2 = 23)

# merge iso2 onto chain_features
chain_features <- chain_features %>%
  left_join(country_by_layer)

```


KI-3
KI-6
Cat-1
Cat-2
SS

for each chain get:
  - average
  - maximum 


SS for BO nationality 
Cat-1 & Cat-2 for iso2 in chain


-if YY in chain, replace each measure with mean of that measure (from FSI data)
- could include a cat variable for BO nationality - not I, GB, not GB
- if guo is not an individual, red-flag


- were those with 0 layers removed - yes
- those with 0 layers removed as some of the features can't be created (those dependent on having an ownership structure).
- those with 0 layers are partially verified through knowing all the chain, and less of a concern to red flag
- this analysis focuses on those with ownership chains

```{r}
# ADD FINANCIAL SECRECY INDEX DATA

secrecy_scores <- secrecy_scores %>%
  select(`ISO-2`, `KI-15`, `KI cat 1`, `KI cat 2`, SS) %>%
  rename(iso2 = 1, cat1 = 2, cat2 = 3, ss = 4, ki15 = 5)

# Replace YY with means
mean_cat1 <- mean(secrecy_scores$cat1, na.rm = T)
mean_cat2 <- mean(secrecy_scores$cat2, na.rm = T)
mean_ki15 <- mean(secrecy_scores$ki15, na.rm = T)
mean_ss <- mean(secrecy_scores$ss, na.rm = T)

# merge score onto chain features
secrecy_scores <- secrecy_scores %>%
  add_case(iso2 = "YY",
         cat1 = mean_cat1,
         cat2 = mean_cat2,
         ki15 = mean_ki15,
         ss = mean_ss)

secrecy_scores <- secrecy_scores %>%
  add_case(iso2 = "ZZ",
         cat1 = mean_cat1,
         cat2 = mean_cat2,
         ki15 = mean_ki15,
         ss = mean_ss)

layer1_secrecy_scores <- secrecy_scores %>%
  rename(layer1_iso2 = 1,
         layer1_cat1 = 2,
         layer1_cat2 = 3,
         layer1_ss = 4,
         layer1_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer1_secrecy_scores)

layer2_secrecy_scores <- secrecy_scores %>%
  rename(layer2_iso2 = 1,
         layer2_cat1 = 2,
         layer2_cat2 = 3,
         layer2_ss = 4,
         layer2_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer2_secrecy_scores)

layer3_secrecy_scores <- secrecy_scores %>%
  rename(layer3_iso2 = 1,
         layer3_cat1 = 2,
         layer3_cat2 = 3,
         layer3_ss = 4,
         layer3_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer3_secrecy_scores)

layer4_secrecy_scores <- secrecy_scores %>%
  rename(layer4_iso2 = 1,
         layer4_cat1 = 2,
         layer4_cat2 = 3,
         layer4_ss = 4,
         layer4_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer4_secrecy_scores)

layer5_secrecy_scores <- secrecy_scores %>%
  rename(layer5_iso2 = 1,
         layer5_cat1 = 2,
         layer5_cat2 = 3,
         layer5_ss = 4,
         layer5_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer5_secrecy_scores)

layer6_secrecy_scores <- secrecy_scores %>%
  rename(layer6_iso2 = 1,
         layer6_cat1 = 2,
         layer6_cat2 = 3,
         layer6_ss = 4,
         layer6_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer6_secrecy_scores)

layer7_secrecy_scores <- secrecy_scores %>%
  rename(layer7_iso2 = 1,
         layer7_cat1 = 2,
         layer7_cat2 = 3,
         layer7_ss = 4,
         layer7_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer7_secrecy_scores)

layer8_secrecy_scores <- secrecy_scores %>%
  rename(layer8_iso2 = 1,
         layer8_cat1 = 2,
         layer8_cat2 = 3,
         layer8_ss = 4,
         layer8_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer8_secrecy_scores)

layer9_secrecy_scores <- secrecy_scores %>%
  rename(layer9_iso2 = 1,
         layer9_cat1 = 2,
         layer9_cat2 = 3,
         layer9_ss = 4,
         layer9_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer9_secrecy_scores)

layer10_secrecy_scores <- secrecy_scores %>%
  rename(layer10_iso2 = 1,
         layer10_cat1 = 2,
         layer10_cat2 = 3,
         layer10_ss = 4,
         layer10_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer10_secrecy_scores)

layer11_secrecy_scores <- secrecy_scores %>%
  rename(layer11_iso2 = 1,
         layer11_cat1 = 2,
         layer11_cat2 = 3,
         layer11_ss = 4,
         layer11_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer11_secrecy_scores)

layer12_secrecy_scores <- secrecy_scores %>%
  rename(layer12_iso2 = 1,
         layer12_cat1 = 2,
         layer12_cat2 = 3,
         layer12_ss = 4,
         layer12_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer12_secrecy_scores)

layer13_secrecy_scores <- secrecy_scores %>%
  rename(layer13_iso2 = 1,
         layer13_cat1 = 2,
         layer13_cat2 = 3,
         layer13_ss = 4,
         layer13_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer13_secrecy_scores)

layer14_secrecy_scores <- secrecy_scores %>%
  rename(layer14_iso2 = 1,
         layer14_cat1 = 2,
         layer14_cat2 = 3,
         layer14_ss = 4,
         layer14_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer14_secrecy_scores)

layer15_secrecy_scores <- secrecy_scores %>%
  rename(layer15_iso2 = 1,
         layer15_cat1 = 2,
         layer15_cat2 = 3,
         layer15_ss = 4,
         layer15_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer15_secrecy_scores)

layer16_secrecy_scores <- secrecy_scores %>%
  rename(layer16_iso2 = 1,
         layer16_cat1 = 2,
         layer16_cat2 = 3,
         layer16_ss = 4,
         layer16_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer16_secrecy_scores)

layer17_secrecy_scores <- secrecy_scores %>%
  rename(layer17_iso2 = 1,
         layer17_cat1 = 2,
         layer17_cat2 = 3,
         layer17_ss = 4,
         layer17_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer17_secrecy_scores)

layer18_secrecy_scores <- secrecy_scores %>%
  rename(layer18_iso2 = 1,
         layer18_cat1 = 2,
         layer18_cat2 = 3,
         layer18_ss = 4,
         layer18_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer18_secrecy_scores)

layer19_secrecy_scores <- secrecy_scores %>%
  rename(layer19_iso2 = 1,
         layer19_cat1 = 2,
         layer19_cat2 = 3,
         layer19_ss = 4,
         layer19_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer19_secrecy_scores)

layer20_secrecy_scores <- secrecy_scores %>%
  rename(layer20_iso2 = 1,
         layer20_cat1 = 2,
         layer20_cat2 = 3,
         layer20_ss = 4,
         layer20_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer20_secrecy_scores)

layer21_secrecy_scores <- secrecy_scores %>%
  rename(layer21_iso2 = 1,
         layer21_cat1 = 2,
         layer21_cat2 = 3,
         layer21_ss = 4,
         layer21_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer21_secrecy_scores)

layer22_secrecy_scores <- secrecy_scores %>%
  rename(layer22_iso2 = 1,
         layer22_cat1 = 2,
         layer22_cat2 = 3,
         layer22_ss = 4,
         layer22_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer22_secrecy_scores)

layer23_secrecy_scores <- secrecy_scores %>%
  rename(layer23_iso2 = 1,
         layer23_cat1 = 2,
         layer23_cat2 = 3,
         layer23_ss = 4,
         layer23_ki15 = 5)
chain_features <- chain_features %>%
  left_join(layer23_secrecy_scores)

	
# CLEAN GUO / BO 

chain_features <- chain_features %>%
  mutate(bo1 = case_when(guo_entity_type != "I" ~ 1, T ~ 0)) %>% # bo1 - not individuals
  mutate(bo2 = case_when((bo1 == 0) & (guo_iso2 != "GB") ~ 1, T ~ 0)) %>% # bo2 - foreign individuals
  mutate(bo3 = case_when((bo1 == 0) & (guo_iso2 == "GB") ~ 1, T ~ 0)) # bo3 - GB individuals



# FILTER FOR COUNTRIES IN FSI
chain_features <- chain_features %>%
  filter(!is.na(layer1_cat1))
  

```



```{r}

# CREATE FSI FEATURES

chain_features_ki15 <- chain_features %>%
  pivot_longer(cols = c(layer1_ki15,
                        layer2_ki15,
                        layer3_ki15,
                        layer4_ki15,
                        layer5_ki15,
                        layer6_ki15,
                        layer7_ki15,
                        layer8_ki15,
                        layer9_ki15,
                        layer10_ki15,
                        layer11_ki15,
                        layer12_ki15,
                        layer13_ki15,
                        layer14_ki15,
                        layer15_ki15,
                        layer16_ki15,
                        layer17_ki15,
                        layer18_ki15,
                        layer19_ki15,
                        layer20_ki15,
                        layer21_ki15,
                        layer22_ki15,
                        layer23_ki15),
               names_to = "ki15_layer",
               values_to = "ki15_score")

chain_features_ki15 <- chain_features_ki15 %>%
  group_by(terminal_bvd) %>%
  summarise(av_ki15 = mean(ki15_score, na.rm = T),
            max_ki15 = max(ki15_score, na.rm = T))

chain_features_cat1 <- chain_features %>%
  pivot_longer(cols = c(layer1_cat1,
                        layer2_cat1,
                        layer3_cat1,
                        layer4_cat1,
                        layer5_cat1,
                        layer6_cat1,
                        layer7_cat1,
                        layer8_cat1,
                        layer9_cat1,
                        layer10_cat1,
                        layer11_cat1,
                        layer12_cat1,
                        layer13_cat1,
                        layer14_cat1,
                        layer15_cat1,
                        layer16_cat1,
                        layer17_cat1,
                        layer18_cat1,
                        layer19_cat1,
                        layer20_cat1,
                        layer21_cat1,
                        layer22_cat1,
                        layer23_cat1),
               names_to = "cat1_layer",
               values_to = "cat1_score")

chain_features_cat1 <- chain_features_cat1 %>%
  group_by(terminal_bvd) %>%
  summarise(av_cat1 = mean(cat1_score, na.rm = T),
            max_cat1 = max(cat1_score, na.rm = T))

chain_features_cat2 <- chain_features %>%
  pivot_longer(cols = c(layer1_cat2,
                        layer2_cat2,
                        layer3_cat2,
                        layer4_cat2,
                        layer5_cat2,
                        layer6_cat2,
                        layer7_cat2,
                        layer8_cat2,
                        layer9_cat2,
                        layer10_cat2,
                        layer11_cat2,
                        layer12_cat2,
                        layer13_cat2,
                        layer14_cat2,
                        layer15_cat2,
                        layer16_cat2,
                        layer17_cat2,
                        layer18_cat2,
                        layer19_cat2,
                        layer20_cat2,
                        layer21_cat2,
                        layer22_cat2,
                        layer23_cat2),
               names_to = "cat2_layer",
               values_to = "cat2_score")

chain_features_cat2 <- chain_features_cat2 %>%
  group_by(terminal_bvd) %>%
  summarise(av_cat2 = mean(cat2_score, na.rm = T),
            max_cat2 = max(cat2_score, na.rm = T))


# SELECT AND MERGE REQUIRED FEATURES

model_features <- chain_features %>%
  select(terminal_bvd,
         num_layers,
         uk_layers_per,
         bo1,
         bo2,
         bo3)

model_features <- model_features %>%
  left_join(chain_features_cat1) %>%
  left_join(chain_features_cat2) %>%
  left_join(chain_features_ki15)



# LATE FILING / SIC

late_filing <- late_filing %>%
  select(3, 9) %>%
  rename(terminal_bvd = 1,
         sic_1 = 2) %>%
  mutate(late_filing = 1)

late_filing <- sic_to_section(late_filing, sic_1, 1)

late_filing <- late_filing %>%
  select(terminal_bvd,
         late_filing,
         sic_section_name_1)

# merge on

model_features <- model_features %>%
  left_join(late_filing)

model_features <- model_features %>%
  mutate(late_filing = case_when(is.na(late_filing) ~ 0, T ~ late_filing))

# export clean data 

write_csv(model_features, here("data/model_features.csv"))


```








# AMALYSIS 1: SECRECY RED FLAGS

Include chain length distribution
include all 3 secrecy measure distributions (add mean, and cut offs)

Red-flags if: 
- if length of chain is top 1% 
- any of 3 secrecy measures is the max
- all of the 3 secrecy measures are top 10%

How many companies red-flagged?
What do there BO features look like, compared to non red-flagged?


```{r}
# PLOT 1 - CHAIN LENGTH DISTRIBUTION  

ggplot(model_features) +
  geom_histogram(aes(x=num_layers), binwidth = 1, fill = "#66c2a5") + 
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("No. of Layers") +
  ylab("No. of Companies")
  
```

```{r}
# PLOT 2 - AV CAT1 DISTRIBUTION  

ggplot(model_features) +
  geom_histogram(aes(x=av_cat1), fill = "#fc8d62") + 
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Mean Category 1 Score") +
  ylab("No. of Companies") +
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))
  
  
```

```{r}
# PLOT 3 - MAX CAT1 DISTRIBUTION 

ggplot(model_features) +
  geom_histogram(aes(x=max_cat1), fill = "#8da0cb") +
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Max Category 1 Score") +
  ylab("") +
 theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))

```

```{r}
# PLOT 4 - AV CAT2 DISTRIBUTION  

ggplot(model_features) +
  geom_histogram(aes(x=av_cat2), fill = "#fc8d62") + 
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Mean Category 2 Score") +
  ylab("No. of Companies") +
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))
  
```

```{r}
# PLOT 5 - MAX CAT2 DISTRIBUTION 

ggplot(model_features) +
  geom_histogram(aes(x=max_cat2), fill = "#8da0cb") +
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Max Category 2 Score") +
  ylab("") +
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))

```

```{r}
# PLOT 6 - AV KI15 DISTRIBUTION  

ggplot(model_features) +
  geom_histogram(aes(x=av_ki15), fill = "#fc8d62") + 
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Mean KFSI-15 Score") +
  ylab("No. of Companies") +
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))
  
```

```{r}
# PLOT 7 - MAX KI15 DISTRIBUTION 

ggplot(model_features) +
  geom_histogram(aes(x=max_ki15), fill = "#8da0cb") +
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  xlab("Max KFSI-15 Score") +
  ylab("") + 
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size=16))

```

```{r}
# FIND RED-FLAG CUT OFFS

analysis1_data <- model_features

# number of layers
quantile(analysis1_data$num_layers, probs = 0.99)
layers_flag <- 8

# cat 1
cat1_flag_max <- max(secrecy_scores$cat1)

quantile(secrecy_scores$cat1, probs = 0.9)
cat1_flag_10 <- 75

# cat 2
cat2_flag_max <- max(secrecy_scores$cat2)

quantile(secrecy_scores$cat2, probs = 0.9)
cat2_flag_10 <- 82.87

# ki15
ki15_flag_max <- max(secrecy_scores$ki15)

quantile(secrecy_scores$ki15, probs = 0.9)
ki15_flag_10 <- 76.075

```

```{r}
# RED-FLAG COMPANIES

analysis1_data <- analysis1_data %>%
  # number of layers
  mutate(red_flag = case_when(num_layers >= layers_flag ~ 1, T ~ 0)) %>%
  # any secrecy measure max
  mutate(red_flag = case_when((max_cat1 == cat1_flag_max) |
                              (max_cat2 == cat2_flag_max) |
                              (max_ki15 == ki15_flag_max) ~ 1, T ~ red_flag)) %>%
  # all secrecy top 10% 
  mutate(red_flag = case_when((max_cat1 == cat1_flag_10) &
                              (max_cat2 == cat2_flag_10) &
                              (max_ki15 == ki15_flag_10) ~ 1, T ~ red_flag))


```

```{r}
# ANALYSIS 

# how many companies flagged?

analysis1_flagged <- analysis1_data %>%
  filter(red_flag == 1)

count(analysis1_flagged)

# % of companies flag

(count(analysis1_flagged)/count(analysis1_data))*100

# BO flagged vs not 
analysis1_bo_summary <- analysis1_data %>%
  group_by(red_flag) %>%
  summarise(bo1 = mean(bo1),
            bo2 = mean(bo2),
            bo3 = mean(bo3))
```


# ANALYSIS 2: OUTLIER RED FLAGS

- Run outlier detection 
- of those that were red-flagged, what do their chain lengths & secrecy measures look like?
- how does this compared to analysis 1? 
- how many were red-flagged?
- what do their BO features look like?
- correlation between those flagged in analysis 1 & those in analysis 2?


Q: do categoricals need to be in dummy form? NO!
- Can adjust the anomaly score threashold to the government agencies discresion
- Could adjust to 3% anomalies then compare?

```{r}

# prepare data
analysis2_data <- model_features %>%
  select(!c(terminal_bvd, late_filing, sic_section_name_1)) %>%
  mutate(bo1 = as_factor(bo1)) %>%
  mutate(bo2 = as_factor(bo2)) %>%
  mutate(bo3 = as_factor(bo3)) 

set.seed(1)

# train model
iso = isolationForest$new(sample_size = nrow(analysis2_data))
iso$fit(analysis2_data)

# get anomaly scores
scores_train <- iso$predict(analysis2_data)

# merge scores to data
analysis2_data <- analysis2_data %>% mutate(id = row_number())
analysis2_data <- analysis2_data %>%
  left_join(scores_train)

# quantiles of anomaly scores
quantile(analysis2_data$anomaly_score, probs = 0.97)
anomaly_flag <- 0.64

# RED FLAG COMPANIES 
analysis2_data <- analysis2_data %>%
  # number of layers
  mutate(red_flag = case_when(anomaly_score >= anomaly_flag ~ 1, T ~ 0))

```

```{r}
# ANALYSIS 

# BO flagged vs not 
analysis2_bo_summary <- analysis2_data %>%
  mutate(bo1 = as.numeric(bo1)-1) %>%
  mutate(bo2 = as.numeric(bo2)-1) %>%
  mutate(bo3 = as.numeric(bo3)-1) %>%
  group_by(red_flag) %>%
  summarise(bo1 = mean(bo1),
            bo2 = mean(bo2),
            bo3 = mean(bo3),
            max_cat1 = mean(max_cat1),
            max_cat2 = mean(max_cat2),
            max_ki15 = mean(max_ki15))

# compare others to flag cut offs in analysis 1
```

```{r}
# PLOT 8 - ANOMALY SCORE
ggplot(analysis2_data) +
  geom_density(aes(x=anomaly_score), fill = "#e78ac3") + 
  scale_x_continuous(limits=c(0.5, 0.8)) +
  geom_vline(xintercept = 0.64, size = 1, colour = "#fc8d62") +
  theme_light() +
  xlab("Anomaly Score") +
  ylab("Density") +
  annotate(geom = "text", x=0.65, y=70, label = "0.64", colour = "#fc8d62")
```





# ANALYSIS 3: LATE-FILING RED-FLAGS

```{r}
# prepare data
analysis3_data <- model_features %>%
  select(!c(sic_section_name_1)) %>%
  mutate(bo1 = as_factor(bo1)) %>%
  mutate(bo2 = as_factor(bo2)) %>%
  mutate(bo3 = as_factor(bo3)) %>%
  mutate(late_filing = as_factor(late_filing))

analysis3_data1 <- analysis3_data %>%

set.seed(2)


# split into test and train sets
sample <- sample.split(analysis3_data$late_filing, SplitRatio = .75)
train_data <- subset(analysis3_data, sample == TRUE)
test_data  <- subset(analysis3_data, sample == FALSE)
dim(train_data)
dim(test_data)

train <- train_data %>%
  select(!c(terminal_bvd))
test <- test_data %>%
  select(!c(terminal_bvd, late_filing))

# train model
rf <- randomForest(late_filing ~ ., data = train, 
                   ntree = 500,
                   mtry = 3)
rf 

# test
pred <- predict(rf, newdata = test)

test_y <- test_data %>% 
  select(late_filing) %>%
  mutate(late_filing = as_factor(late_filing))

pred_y <- data_frame(pred) %>%
  mutate(pred = as_factor(pred))

result <- cbind(pred_y, test_y)

result <- result %>%
  mutate(error = case_when(pred != late_filing ~ 1, T ~ 0))

(sum(result$error)/nrow(result))*100


# summary of those late-filing
analysis3_bo_summary <- analysis3_data %>%
  mutate(bo1 = as.numeric(bo1)-1) %>%
  mutate(bo2 = as.numeric(bo2)-1) %>%
  mutate(bo3 = as.numeric(bo3)-1) %>%
  mutate(late_filing = as.numeric(late_filing)-1) %>%
  group_by(late_filing) %>%
  summarise(bo1 = mean(bo1),
            bo2 = mean(bo2),
            bo3 = mean(bo3),
            max_cat1 = mean(max_cat1),
            max_cat2 = mean(max_cat2),
            max_ki15 = mean(max_ki15))
```
- error rate of 4.67%
- good algorithm as non-parametric
- need other features

```{r}
# RED-FLAG OVERLAPS

flag_1 <- analysis1_data %>%
  select(terminal_bvd, red_flag) %>%
  filter(terminal_bvd %in% test_data$terminal_bvd) %>%
  mutate(red_flag_1 = red_flag) %>%
  select(!red_flag)

final_terminal_bvd <- model_features %>%
  select(terminal_bvd)

flag_2 <- cbind(final_terminal_bvd, analysis2_data) %>%
  select(terminal_bvd, red_flag) %>%
  filter(terminal_bvd %in% test_data$terminal_bvd) %>%
  mutate(red_flag_2 = red_flag) %>%
  select(!red_flag)
  
flag_3 <- cbind(pred_y, test_data) %>%
  select(terminal_bvd, pred) %>%
  mutate(red_flag_3 = as.numeric(pred)-1) %>%
  select(!pred)

all_flags <- flag_1 %>%
  left_join(flag_2) %>%
  left_join(flag_3)

all_flags <- all_flags %>%
  mutate(red_flag_12 = case_when((red_flag_1 == 1) & (red_flag_2 == 1) ~ 1, T ~ 0)) %>%
  mutate(red_flag_13 = case_when((red_flag_1 == 1) & (red_flag_3 == 1) ~ 1, T ~ 0)) %>%
  mutate(red_flag_23 = case_when((red_flag_2 == 1) & (red_flag_3 == 1) ~ 1, T ~ 0)) %>%
  mutate(red_flag_123 = case_when((red_flag_1 == 1) &
                                  (red_flag_2 == 1) & 
                                  (red_flag_3 == 1) ~ 1, T ~ 0))
all_flags_summary <- all_flags %>%
  summarise(red_flag_1 = sum(red_flag_1)/nrow(all_flags)*100,
            red_flag_2 = sum(red_flag_2)/nrow(all_flags)*100,
            red_flag_3 = sum(red_flag_3)/nrow(all_flags)*100,
            red_flag_12 = sum(red_flag_12)/nrow(all_flags)*100,
            red_flag_13 = sum(red_flag_13)/nrow(all_flags)*100,
            red_flag_23 = sum(red_flag_23)/nrow(all_flags)*100,
            red_flag_123 = sum(red_flag_123)/nrow(all_flags)*100)
```




